Title here

### 2016-09-09 portfolio/text/ms.Rmd
Calculate effect sizes for abstracts and results...
Also switch to 95% CIs where possible
Edits to text

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(cache=TRUE, echo=FALSE, message=FALSE, autodep=TRUE,
  results='hide')
opts_chunk$set(warning=FALSE, message=FALSE, cache.path="../cache/",
  cache.lazy=TRUE)
```
```{r get-dat, cache=FALSE}
load("../data-generated/output-values.rda")
```

@@

Individuals relying on natural resources as their primary source of income
often experience high levels of income variability
due to the combined effects of environmental, biological, and price variation.
Commercial fishers are a prime example and
recent work has sought to identify regulations and fishing behaviours
that can reduce this variability.
A top candidate has been that fishing higher levels of species diversity
decreases income variability.
However, it is unknown if this species-diversity effect
on income variability holds
across multiple approaches to diversifying catch,
at the level of individual permit holders,
and across different fishing strategies.
Here, we simultaneously estimate the effects of three
methods of diversification for Alaskan fishery permit holders
on revenue and revenue variability:
(1) owning multiple permits,
(2) owning permits that inherently fish higher species diversity,
and (3) increasing species diversity within the constraints of a permit set.
We control for changes in effort and other
latent effects through time.
We find that
fishing an additional permit is associated with
lower variability (~XX--XX%) and higher revenue,
fishing permits with higher species diversity reduces risk
(XX% [XX--XX 95% CI] per unit increase in mean Simpson's diversity index),
but that increasing species diversity within
the constraints of a permit set has a fishery-dependent effect on revenue and
is usually (XX%) associated with increased revenue variability.
At the same time, Alaskan commercial fisheries
have been increasingly focussed on
single-permit (often salmon) fishing strategies
with single-permit fishers earning
more than multiple-permit fishers
for the first time in 2013.
Our results suggest that the benefit of species diversity
on reducing revenue variability
is mostly an across-permit effect, not
a benefit that can be easily harnessed by an individual permit holder.
Effective methods of diversification ---
purchasing additional permits or switching permits ---
are costly and often limited by regulations such as limited entry
programs and individual transferable quotas (ITQs).
Take home ...

@@

<!-- write out each paragraph’s main message in 15 words or less -->

<!-- circulate skeleton ... this is the time to fix problems with flow, -->
<!-- ideas/content, main message -->

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Diversifying permits reduces risk and usually increases revenue.
Two examples of expected revenue variability
and median revenue for
owners of (A) individual halibut and (B) gillnet herring roe permits
(light blue)
compared with owners of the same permit plus one more (medium blue)
or two more permits (dark blue).
On the y-axis, dots and lines represent posterior median and 90\%
credible intervals.}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Individuals who fish
permits and permit combinations (permit strategies) with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common permit strategies.
Thick black line, and dark and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strategy-level regression built into the hierarchical model.
Estimated variability represents expected standard deviation
at an average of about
`r mean_permit_days` combined fishing days across permits,
and for a permit holder who does not change
species diversity or days fished from year to year.
}
\label{fig:across}
\end{center}
\end{figure}

>>>>

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(cache=TRUE, echo=FALSE, message=FALSE, autodep=TRUE,
  results='hide')
opts_chunk$set(warning=FALSE, message=FALSE, cache.path="../cache/",
  cache.lazy=TRUE)
```
```{r get-dat, cache=FALSE}
load("../data-generated/output-values.rda")
h1 <- readRDS("../data-generated/h1_effect.rds")
spoke <- readRDS("../data-generated/spoke_fraction.rds")
g2_dens <- readRDS("../data-generated/g2_prob_dens_above_zero.rds")
```

@@

Individuals relying on natural resources as their primary source of income
often experience high levels of income variability
due to the combined effects of environmental, biological, and price variation.
Commercial fishers are a prime example and
recent work has sought to identify regulations and fishing behaviours
that can reduce this variability.
A top candidate has been that fishing higher levels of species diversity
decreases income variability.
However, it is unknown if this species-diversity effect
on income variability holds
across multiple approaches to diversifying catch,
at the level of individual permit holders,
and across different fishing strategies.
Here, we simultaneously estimate the effects of three
methods of diversification for Alaskan fishery permit holders
on revenue and revenue variability:
(1) owning multiple permits,
(2) owning permits that inherently fish higher species diversity,
and (3) increasing species diversity within the constraints of a permit set.
We control for changes in effort and other
latent effects through time.
We find that
fishing an additional permit is associated with higher revenue
and lower variability (e.g., 
`r 100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR] lower
expected standard deviation for halibut permit holders), 
fishing permits with higher species diversity reduces variability
(`r h1[[2]]`% [`r h1[[1]]`--`r h1[[3]]`% 95% CI] reduction per unit 
increase in mean Simpson's diversity index),
but that increasing species diversity within
the constraints of a permit set has a fishery-dependent effect on revenue and
is usually (`r g2_dens`% of probability density) 
associated with increased revenue variability.
At the same time, Alaskan commercial fisheries
have been increasingly focussed on
single-permit (often salmon) fishing strategies
with single-permit fishers earning
more than multiple-permit fishers
for the first time in 2013.
Our results suggest that the benefit of species diversity
on reducing revenue variability
is mostly an across-permit effect, not
a benefit that can be easily harnessed by an individual permit holder.
Effective methods of diversification ---
purchasing additional permits or switching permits ---
are costly and often limited by regulations such as limited entry
programs and individual transferable quotas (ITQs).
Take home ...

@@

<!-- write out each paragraph’s main message in 15 words or less -->
<!-- circulate skeleton ... this is the time to fix problems with flow, -->
<!-- ideas/content, main message -->

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Diversifying permits reduces risk and usually increases revenue.
Two examples of expected revenue variability
and median revenue for
owners of (A) individual halibut and (B) gillnet herring roe permits
(dark blue)
compared with owners of the same permit plus one more (medium blue)
or two more permits (light blue).
On the y-axis, dots and lines represent posterior median and 95\%
credible intervals of expected standard deviation.}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability2.pdf}
\caption{Individuals who fish
permits and permit combinations (permit strategies) with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common permit strategies.
Thick black line, and dark and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strategy-level regression built into the hierarchical model.
Estimated variability represents expected standard deviation
for a permit holder who does not change
species diversity or days fished from year to year
with the strategy-level effect of mean days fished removed.
}
\label{fig:across}
\end{center}
\end{figure}
